ANALYZING "Why do people play violent video games? Demographic, status-related, and mating-related correlates in men and women"
========================================================

General housekeeping
--------------------

First load the libraries that we are using
```{r}
library(ggplot2)
library(knitr)
library(plyr)
library(QuantPsyc)
library(PerformanceAnalytics)
library(heplots)
library(gridExtra)
library(mediation)
```

Next load the functions that we'll use for summary data

Using the script written here: http://www.r-bloggers.com/more-on-exploring-correlations-in-r/
to create the correlation data for the table, but also to create a figure of correlation values

See http://goo.gl/nahmV for documentation of this function
```{r}
cor.prob <- function (X, dfr = nrow(X) - 2) {
  R <- cor(X, use="pairwise.complete.obs")
  above <- row(R) < col(R)
  r2 <- R[above]^2
  Fstat <- r2 * dfr/(1 - r2)
  R[above] <- 1 - pf(Fstat, 1, dfr)
  R[row(R) == col(R)] <- NA
  R
}
```

Use this function to dump the cor.prob output to a 4 column matrix with row/column indices, correlation, and p-value. See StackOverflow question: http://goo.gl/fCUcQ

```{r}
flattenSquareMatrix <- function(m) {
  if( (class(m) != "matrix") | (nrow(m) != ncol(m))) stop("Must be a square matrix.") 
  if(!identical(rownames(m), colnames(m))) stop("Row and column names must be equal.")
  ut <- upper.tri(m)
  data.frame(i = rownames(m)[row(m)[ut]],
             j = rownames(m)[col(m)[ut]],
             cor=t(m)[ut],
             p=m[ut])
}
```

Use this one for summary statistics

```{r}
my.summary <- function(x, na.rm=TRUE){
  result <- c(Mean=mean(x, na.rm=na.rm),
              SD=sd(x, na.rm=na.rm),
              Median=median(x, na.rm=na.rm),
              Min=min(x, na.rm=na.rm),
              Max=max(x, na.rm=na.rm), 
              N=length(x))
}
```

Load the data (VVG_data.csv).
Note the as.is thing which leaves all the character vectors as strings and does not make them into factors.

```{r}
data = read.table(file.choose(),  na.strings =".", header=T, sep=",")
```

Attach and check the headers of each column

```{r}
attach(data)
names(data)
```

Recode gender into numerical values

```{r}
data$Gender2 <- revalue(data$Gender, c("Male"="1", "Female"="2"))
data$Gender2 <- as.numeric(as.character(data$Gender2))
```

Ensuring that certain columns are treated as categorical

```{r}
data$RelStat <- factor(data$RelStat)
data$Sexuality <- factor(data$Sexuality)
data$Education <- factor(data$Education)
```

Then log transform CTS as it is right skewed, and create a new 'Income' variable

```{r}
data$CTSlog <- log(data$CTS+1)
data$Income <- (data$FutureIncome + data$CurrentIncome)/2
```

Delete Rows that are missing values in the ESRB Ratings, MateValue1, SOI & Leadership

```{r}
data<-data[-which(is.na(data$PlayXESRB_mean)),]
data<-data[-which(is.na(data$MV1)),]
data<-data[-which(is.na(data$SOI)),]
data<-data[-which(is.na(data$Leadership)),]
```

Then subset data by Study

```{r}
mturk1 = subset(data, Study=="Mturk1")
mturk2 = subset(data, Study=="MTurk2")
```

Remove individuals that have a relationship status of 'other' (2 individuals in each replicate)

```{r}
mturk1 = subset(mturk1, RelStat %in% c("1", "2", "3", "4"))
mturk2 = subset(mturk2, RelStat %in% c("1", "2", "3", "4"))
```


Explore 'MTurk1'
---------------

What is the mean, SD and range of the age of respondents in the first sample?
```{r}
mean(mturk1$Age)
sd(mturk1$Age)
range(mturk1$Age)
```

Get the correlation between current and expected future earnings
```{r}
cor.test(mturk1$CurrentIncome,mturk1$FutureIncome)
```

What is the mean, SD of the age of respondents in the first sample?
```{r}
mean(mturk1$Height)
sd(mturk1$Height)

mean(mturk1$Weight)
sd(mturk1$Weight)

mean(mturk1$Strength, na.rm=TRUE)
sd(mturk1$Strength, na.rm=TRUE)

mean(mturk1$BodyShape, na.rm=TRUE)
sd(mturk1$BodyShape, na.rm=TRUE)
```

get the columns that you want from the dataset then create a correlation matrix
then get the p-values using the above function "flatten" that table using the above function
This will collect the data for Table S1

```{r}
corrmturk1 <- mturk1[, c(35,10,6,8,37,3,5,7,11)]
cor(corrmturk1)
cor.prob(corrmturk1)
flattenSquareMatrix(cor.prob(corrmturk1))
```

Finally, plot the data using, but turn off warnings first
```{r}
options(warn=-1)
chart.Correlation(corrmturk1)
```

Now to get the meands and SDs for the above selected columns using my.summary function

```{r}
sapply(corrmturk1, my.summary)  
```

and then the numbers in each of the categorical groups

```{r}
table(mturk1$Education)
table(mturk1$Sexuality)
table(mturk1$RelStat)
```

Do men and women differ in the amount of violent video games they play (self-rated)

```{r}
VVGsexM1 <- t.test(PlayXViolence_mean ~ Gender, data = mturk1)
VVGsexM1

ddply(mturk1, c("Gender"), summarise,
               N    = length(PlayXViolence_mean),
               mean = mean(PlayXViolence_mean),
               sd   = sd(PlayXViolence_mean),
               se   = sd / sqrt(N)
)
```

Yes they do; women play less violent games. 

Now make a histogram of the overlap in violent video game play between the sexes (Figure S1)
```{r}
hist1 <- ggplot(mturk1, aes(x=PlayXViolence_mean, fill=Gender)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "none",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

hist1
```

Here are the models for creating Table 1 and Table S2

First, relevel the coefficients
```{r}
mturk1$RelStat <-relevel(mturk1$RelStat, "2")
mturk1$Sexuality <-relevel(mturk1$Sexuality, ref = "3")
mturk1$Education <-relevel(mturk1$Education, ref = "1")
```

Here is the full model

```{r}
VGplayself.all.mturk1<-lm(PlayXViolence_mean ~ MV1 + SOI + LeadershipDom + WordSum + CTSlog + Sexuality + RelStat + Income + Education + Gender + Age + Gender*MV1 + Gender*SOI + Gender*LeadershipDom + Gender*WordSum + Gender*CTSlog + Gender*Sexuality + Gender*RelStat + Gender*Income + Gender*Education, data=mturk1)

anova(VGplayself.all.mturk1, test="typeIII")
summary(VGplayself.all.mturk1)

etasq(VGplayself.all.mturk1)
```

calculate r-squared for relationship between SOI & MV with VVGExposure

```{r}
cor.test(mturk1$PlayXViolence_mean,mturk1$SOI)

mturk1.fem = subset(mturk1, Gender=="Female")
cor.test(mturk1.fem$PlayXViolence_mean,mturk1.fem$MV1)

mturk1.mal = subset(mturk1, Gender=="Male")
cor.test(mturk1.mal$PlayXViolence_mean,mturk1.mal$MV1)
```

Here is Figure S2
```{r}
plotSOI1 <- ggplot(mturk1, aes(x = SOI, y = PlayXViolence_mean, color = Gender, shape = Gender, linetype = Gender)) + 
  geom_point(size=4) +
  ylim(0,50) +
  scale_colour_hue(l=50, guide = FALSE) +
  scale_x_continuous(limits=c(0,80)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Sexual Interest") +
  ylab("Violent Video Game Exposure") +
  theme(legend.position="none") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

plotSOI1
```

Figure S3
Boxplot of VVGplay with education  (Self-reported)

```{r}
BoxEDU1 <- ggplot(mturk1, aes(x=Education, y=PlayXViolence_mean)) + geom_boxplot() + 
  guides(fill=FALSE) + 
  xlab("Level of Education") +
  ylab("Self-Rated Violence Exposure") +
  scale_x_discrete(labels=c("Primary", "High School", "Vocational", "University", "Post-Graduate"))+
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

BoxEDU1
```

Figure 1
Plot Mate Value and VVGplay for each gender

```{r}
plotMV1 <- ggplot(mturk1, aes(x = MV1, y = PlayXViolence_mean, color = Gender, shape = Gender, linetype = Gender)) + 
  geom_point(size = 4) + 
  ylim(0,50) +
  scale_colour_hue(l=50, guide = FALSE) +
  scale_x_continuous(limits=c(0.5,7.5), breaks=c(1:7)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Mate Value") +
  ylab("Violent Video Game Exposure") +
  theme(legend.position="none") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
plotMV1
```


Here are the exploratory analyses to examine the relationship between gameplay and the number of kids
Next, I'm going to look at Kids, NumberGirls, NumberBoys, NumberTeenageBoys, KidsAge_mean, TeenageBoys_Binary.

but first I'll cut out the individuals that were never married as those individuals skew things at zero.

```{r}
mturk1Kids = subset(mturk1, RelStat %in% c("1", "3"))

VGplayself.family.mturk1<-lm(PlayXViolence_mean ~ NumberBoys + NumberGirls + Gender + Gender*NumberBoys + Gender*NumberGirls, data=mturk1Kids)

anova(VGplayself.family.mturk1, test="Chisq")
```


Explore 'MTurk2'
----------------

What is the mean, SD and range of the age of respondents in the first sample?
```{r}
mean(mturk2$Age)
sd(mturk2$Age)
range(mturk2$Age)
```

What is the mean, SD of the age of respondents in the first sample?
```{r}
mean(mturk2$Height)
sd(mturk2$Height)

mean(mturk2$Weight)
sd(mturk2$Weight)

mean(mturk2$Strength, na.rm=TRUE)
sd(mturk2$Strength, na.rm=TRUE)

mean(mturk2$BodyShape, na.rm=TRUE)
sd(mturk2$BodyShape, na.rm=TRUE)
```

Get the correlation between current and expected future earnings
```{r}
cor.test(mturk2$CurrentIncome,mturk2$FutureIncome)
```

Collect the information for Table S3
Again, use the same function as above to get a table and figure of correlation values

```{r}
corrmturk2 <- mturk2[, c(35,10,6,8,37,4,5,15,11)]
cor(corrmturk2)
cor.prob(corrmturk2)
flattenSquareMatrix(cor.prob(corrmturk2))
```

Finally, plot the data
```{r}
chart.Correlation(corrmturk2)
```

Now to get the means and SDs for the above selected columns using my.summary function

```{r}
sapply(corrmturk2, my.summary)  
```

and then the numbers in each of the categorical groups

```{r}
table(mturk2$Education)
table(mturk2$Sexuality)
table(mturk2$RelStat)
```

Do men and women differ in the amount of violent video games they play (self-rated)

```{r}
VVGsexM2 <- t.test(PlayXViolence_mean ~ Gender, data = mturk2)
VVGsexM2

ddply(mturk2, c("Gender"), summarise,
               N    = length(PlayXViolence_mean),
               mean = mean(PlayXViolence_mean),
               sd   = sd(PlayXViolence_mean),
               se   = sd / sqrt(N)
)
```

Yes they do; women play less violent games. 

Here is the second half of Figure S1
Now make a histogram of the overlap in violent video game play between the sexes
```{r}
hist2 <- ggplot(mturk2, aes(x=PlayXViolence_mean, fill=Gender)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position=c(1,1),legend.justification=c(1,1)) 

hist2
```

relevel the coefficients
```{r}
mturk2$RelStat <-relevel(mturk2$RelStat, "2")
mturk2$Sexuality <-relevel(mturk2$Sexuality, ref = "3")
mturk2$Education <-relevel(mturk2$Education, ref = "1")
```

Here is the full model WITHOUT game motivation

```{r}
VGplayself.all1.mturk2<-lm(PlayXViolence_mean ~ Mvall + SOI + LeadershipDom + WordSum + Sexuality + RelStat + Income + Education + Gender + Age + Gender*Mvall + Gender*SOI + Gender*LeadershipDom + Gender*WordSum + Gender*Sexuality + Gender*RelStat + Gender*Income + Gender*Education, data=mturk2)

anova(VGplayself.all1.mturk2, test="Chisq")
summary(VGplayself.all1.mturk2)

etasq(VGplayself.all1.mturk2)
```

calculate r-squared for relationship between SOI & MV with VVGExposure

```{r}
cor.test(mturk2$PlayXViolence_mean,mturk2$SOI)

mturk2.fem = subset(mturk2, Gender=="Female")
cor.test(mturk2.fem$PlayXViolence_mean,mturk2.fem$Mvall)

mturk2.mal = subset(mturk2, Gender=="Male")
cor.test(mturk2.mal$PlayXViolence_mean,mturk2.mal$Mvall)

cor.test(mturk2$PlayXViolence_mean,mturk2$Age)
```

Here is the second half of Figure S2
Now plot SOI
```{r}
plotSOI2 <- ggplot(mturk2, aes(x = SOI, y = PlayXViolence_mean, color = Gender, shape = Gender, linetype = Gender)) + 
  geom_point(size=4) +
  ylim(0,50) +
  scale_colour_hue(l=50, guide = FALSE) +
  scale_x_continuous(limits=c(0,80)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Sexual Interest") +
  ylab(NULL) +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position=c(.90,.10)) 
plotSOI2
```

Here is the second half of Figure S3
Boxplot of VVGplay with education  (Self-reported)

```{r}
BoxEDU2 <- ggplot(mturk2, aes(x=Education, y=PlayXViolence_mean)) + geom_boxplot() + 
  guides(fill=FALSE) + 
  xlab("Level of Education") +
  ylab(NULL) +
  scale_x_discrete(labels=c("Primary", "High School", "Vocational", "University", "Post-Graduate"))+
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

BoxEDU2
```

Here is the second half of Figure 1
Plot Mate Value and VVGplay for each gender

```{r}
plotMV2 <- ggplot(mturk2, aes(x = Mvall, y = PlayXViolence_mean, color = Gender, shape = Gender, linetype = Gender)) + 
  geom_point(size=4) +
  ylim(0,50) +
  scale_colour_hue(l=50, guide = FALSE) +
  scale_x_continuous(limits=c(0.5,7.5), breaks=c(1:7)) +
  theme_bw() + geom_smooth(method=lm, fullrange=T) + 
  xlab("Mate Value") +
  ylab(NULL) +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position=c(.90,.10)) 

plotMV2
```

Here is the full model WITH game motivation

```{r}
VGplayself.all2.mturk2<-lm(PlayXViolence_mean ~ Mvall + SOI + LeadershipDom + WordSum + Sexuality + RelStat + Income + Education + log(GameMotivation_mean) + Gender + Age + Gender*Mvall + Gender*SOI + Gender*LeadershipDom + Gender*WordSum + Gender*Sexuality + Gender*RelStat + Gender*Income + Gender*Education + Gender*log(GameMotivation_mean), data=mturk2)

anova(VGplayself.all2.mturk2, test="Chisq")
summary(VGplayself.all2.mturk2)

etasq(VGplayself.all2.mturk2)
```

calculate r-squared for relationship between mating motivations & VVGExposure

```{r}
cor.test(mturk2.fem$PlayXViolence_mean,mturk2.fem$GameMotivation_mean)

cor.test(mturk2.mal$PlayXViolence_mean,mturk2.mal$GameMotivation_mean)
```

Figure 2
Now plot game_motivation
```{r}
ggplot(mturk2, aes(x = GameMotivation_mean, y = PlayXViolence_mean, color = Gender, shape = Gender, linetype = Gender)) + 
  geom_point(size=4) +
  theme_bw() + geom_smooth(method=lm, fullrange=T) + 
  scale_colour_hue(l=50, guide = FALSE) +
  ylim(0,50) +
  scale_x_continuous(limits=c(0.75,7.25), breaks=c(1:7)) +
  xlab("Gaming Motivation") +
  ylab("Violent Video Game Exposure") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position=c(.90,.10)) 

```


Figure 1
Now, plot both MV figures together
```{r}
grid.arrange(plotMV1, plotMV2, ncol=2)
g <- arrangeGrob(plotMV1, plotMV2, ncol=2)
ggsave(file="MateValue.tiff",g)
```

Figure S1
Now, plot both histograms of violent videogame play together
```{r}
grid.arrange(hist1, hist2, ncol=2)
g <- arrangeGrob(hist1, hist2, ncol=2)
ggsave(file="histogram.jpg",g)
```

Figure S2
Now, plot both figures together
```{r}
grid.arrange(plotSOI1, plotSOI2, ncol=2)
g <- arrangeGrob(plotSOI1, plotSOI2, ncol=2)
ggsave(file="SOI.eps",g)
```

Figure S3
And now both boxplots of education together
```{r}
grid.arrange(BoxEDU1, BoxEDU2, ncol=2)
g <- arrangeGrob(BoxEDU1, BoxEDU2, ncol=2)
ggsave(file="Education.tiff",g)
```


Supplementary Materials
-----------------------

Here is the full model with age and all the interactions for Mturk 1

```{r}
VGplayself.all.mturk1<-lm(PlayXViolence_mean ~ MV1 + SOI + LeadershipDom + WordSum + CTSlog + Sexuality + RelStat + Income + Education + Gender + Age + Gender*MV1 + Gender*SOI + Gender*LeadershipDom + Gender*WordSum + Gender*CTSlog + Gender*Sexuality + Gender*RelStat + Gender*Income + Gender*Education + Age*MV1 + Age*SOI + Age*LeadershipDom + Age*WordSum + Age*CTSlog + Age*Sexuality + Age*RelStat + Age*Income + Age*Education, data=mturk1)

anova(VGplayself.all.mturk1, test="Chisq")
summary(VGplayself.all.mturk1)
```

and now for Mturk 2

```{r}
VGplayself.all.mturk2<-lm(PlayXViolence_mean ~ Mvall + SOI + WordSum + Sexuality + RelStat + Income + Education + Gender + Age + Gender*Mvall + Gender*SOI + Gender*WordSum + Gender*Sexuality + Gender*RelStat + Gender*Income + Gender*Education + Age*Mvall + Age*SOI + Age*WordSum + Age*Sexuality + Age*RelStat + Age*Income + Age*Education, data=mturk2)

anova(VGplayself.all.mturk2, test="Chisq")
summary(VGplayself.all.mturk2)
```


Here are the correlations and analyses between ESRB ratings and self-perceived ratings


For MTurk 1
Let's see how men and women vary in their ratings of violent games (Self-reported) compared to an objective measure (ESRB)

```{r}
VVGcorrM1 <- lm(PlayXViolence_mean ~ PlayXESRB_mean + Gender, data = mturk1)
anova(VVGcorrM1, test="Chisq")
cor.test(mturk1$PlayXViolence_mean, mturk1$PlayXESRB_mean)
```

So gender has an effect on the correlation. Next, plot VVG correlation between ESRB and self-reported rating with gender as a factor and a 1:1 line 

```{r}
ggplot(mturk1, aes(x = scale(PlayXESRB_mean, center = FALSE, scale = TRUE), y = scale(PlayXViolence_mean, center = FALSE, scale = TRUE), color = Gender)) + geom_point(shape=1, size=4) +
  theme_bw() + geom_smooth(method=lm, se=FALSE, fullrange=T) + 
  xlab("ESRB rating") +
  ylab("Self-reported violence exposure") + geom_abline(intercept = 0, slope = 1, linetype = 2) +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```


For MTurk 2

```{r}
VVGcorrM2 <- lm(PlayXViolence_mean ~ PlayXESRB_mean + Gender, data = mturk2)
anova(VVGcorrM2, test="Chisq")
cor.test(mturk2$PlayXViolence_mean, mturk2$PlayXESRB_mean)
```

So gender has an effect on the correlation. Next, plot VVG correlation between ESRB and self-reported rating with gender as a factor and a 1:1 line 

```{r}
ggplot(mturk2, aes(x = scale(PlayXESRB_mean, center = FALSE, scale = TRUE), y = scale(PlayXViolence_mean, center = FALSE, scale = TRUE), color = Gender)) + geom_point(shape=1, size=4) +
  theme_bw() + geom_smooth(method=lm, se=FALSE, fullrange=T) + 
  xlab("ESRB rating") +
  ylab("Self-reported violence exposure") + geom_abline(intercept = 0, slope = 1, linetype = 2) +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```